### 2021-11-06 paper/manuscript.Rmd
Update Manuscript Results

# Results
There were 20 cases out of 388800 that had missing values on all metrics for the RMA algorithm. Closer inspection showed that both the cubic and exponential model each contributed 10 times to the missing values and only when 2, 3 or 6 moderators were taken up in the model. However, since this makes up 0.005% of the data, the missing values were chosen to be omitted from further analysis. Another thing is that the two-way interaction model only has results when there were either 3,4 or 7 moderators taken up, while the other models only have results when there were 2,3 or 6 moderators. The effects of the moderators is therefore difficult to compare between the two-way interaction and the other models.

*Predictive performance*
Because the densities for the $R^{2}$ and $MSE$ values were skewed, it was chosen to use the median as the metric for predictive performance, rather than the mean. The spread of the data was described using the Mean Absolute Deviation [MAD], rather than the standard deviation. It was found that the Horseshoe, Lasso and RMA algorithm performed similarly overall, $R^2_{hs} = 0.51 \pm 0.36$, $MSE_{hs} = 0.21 \pm 0.18$ ; $R^2_{Lasso} = 0.50 \pm 0.37$, $MSE_{Lasso} = 0.21\pm 0.19$; $R^2_{RMA} = 0.50 \pm 0.37$, $MSE_{RMA} = 0.22 \pm 0.23$ . The random forest algorithm performed worst on $R^2$ $R^2_{rf} = 0.35 \pm 0.38$, $MSE_{rf} = 0.22 \pm 0.19$

To determine the effect of the design factors on predictive performance $R^2$ of all algorithms, four separate ANOVA’s were performed. The effect size $\eta^{2}$ per condition per algorithm, including interactions can be found in table 1. Do note that the ANOVA's were performed with the normality assumption violated. The estimates serve as a guidance, rather than an non-contestable result.

Not too surprisingly, It was found that the true effect size $\beta$ had the largest effect on the predictive $R^{2}$ for all algorithms. As $\beta$ increased, the performance of all algorithms increased as well. However, $\beta$ did seem to interact with the model that was estimated, being either a linear, two-way interaction, cubic or an exponential model. The image of the interaction is shown in image 1. For the exponential and cubic model, the increase of $R^{2}$ slows for every higher value for $\beta$. The two-way interaction model only slows the increase when the es goes from 0.5 to 0.8, while the steepest increase for the linear model is when $\beta$ increases from 0.2 to 0.4. Also noteworthy is that the cubic model seems to stagnate as the effect size goes up to 0.4 and onwards, while the other models do keep increasing. There seemed to be little difference in performance between Horsehoe, Lasso and RMA, while MetaForest performed worst.

The second largest marginal effect was that of the estimated model. It seemed that all algorithms performed best under the cubic model, followed by a similar performance on the two-way interaction and exponential models. All algorithms seemed to perform worst for the linear model. There again is little difference in performance between the Pema algorithms and RMA, altough MetaForest performs worst. Image 2 shows the relationship.

There also was a moderate interaction effect between the estimated model and the amount of skewness of the data [$\alpha$], especially for the Pema algorithms. Again, Pema and RMA algorithms performed best, followed by MetaForest in all conditions. Most obvious to note is that all, except the linear model seem to benefit when the $R^{2}$ was estimated on more skewed data, although the algorithms do perform worse for the interaction model and $\alpha$ goes from 5 to 10. The cubic model performs best overall, but is getting caught up by the exponential and interactoin model as $\alpha$ increases. Image 3 shows the relationship.

The true residual heterogeneity $\tau^{2}$ had a negative linear relationship for all algorithms on $R^{2}$. i.e. as $\tau^{2}$ increases, $R^{2}$ decreased. Image 4 shows the relationship.

The mean sample size per study [$\bar{n}$] also had a moderate effect. For all algorithms the effect of $\bar{n}$ was positively linearly related to $R^{2}$ with the Pema and RMA algorithms performing best and Metaforest performing worst. Image 5 shows the relationship.

An especially large effect was found for the number of studies used in the training data for MetaForest, $\eta^{2}$ = 0.27, while this effect was substantially smaller for RMA, $\eta^{2}$ = 0.11; Lasso, $\eta^{2}$ = 0.06 and; Horseshoe, $\eta^{2}$ = 0.05. The relationship is positively linear for all algorithms, but the slope is especially steep for MetaForest. Image 6 shows the relationship.

Finally, the number of moderators did not have a big effect for the Pema algorithms, $\eta^{2}$ = 0.01 for both Horseshoe and Lasso while for RMA and Metaforest $\eta^{2}$ = 0.05. This relationship is generally negative with more moderators meaning worse performance, although an increase can be observed as the number of moderators increase from 4 to 6 for all algorithms except Metaforest. This increase in performance for Metaforest appears when the number of moderators go from 3 to 4. Image 7 and $\eta^{2}$ values indicate that the Pema algorithms are more robust against number of moderators than RMA and MetaForest.

*Estimating residual heterogeneity* ($\tau^{2}$)
The ability of the algorithms to correctly estimate $\tau^{2}$ was operationalized by subtracting the true value for $\tau^{2}$ from the $\tau^{2}$ estimated by the algorithms. Again, the median and MAD were used as metrics for performance. The RMA algorithm showed the best results, $\Delta\tau^2_{RMA} = 0.02 \pm 0.06$, followed by the Metaforest algorithm $\Delta\tau^2_{MF} = 0.09 \pm 0.13$. The Pema algorithms performed worst $\Delta\tau^2_{Lasso} = 0.23 \pm 0.18$; $\Delta\tau^2_{hs} = 0.23 \pm 0.17$. The finding that all medians are positive implies that all algorithms have a bigger tendency to overestimate $\tau^{2}$ than underestimate it. One comment to make is that uncertainty of the estimates generally increased as $\Delta\tau^{2}$ also increased. This implies that there is more variation in performance as median performance worsens.

To determine the effect of the design factors on estimated $\tau^{2}$ of all algorithms, four separate ANOVA’s were performed. The effect size $\eta^{2}$ per condition per algorithm, including interactions can be found in table 2. Again, the assumption of normality was violated.

The estimated model had one of the biggest effect on the correct estimation of $\tau^{2}$. This is mainly because the algorithms overestimate $\tau^{2}$ quite severely when the model contains cubic relationships. Image 8 shows the marginal relationship of the estimated model on $\Delta\tau^{2}$ . It becomes more clear why this overestimation occurs when showing the interaction between the effect size and the model estimated on $\Delta\tau^{2}$ shown in image 9. First note the general trend which seems to be that for all models, except the linear, $\tau^{2}$ gets more overestimated the higher the true effect size is. This is not the case for the linear algorithm, where the effect of $\beta$ on $\Delta\tau^{2}$  seems close to zero, except for MetaForest. However, note the scales for the y-axes. While the interaction, linear and stay well within a confined interval, the algorithms severely overestimate $\tau^{2}$ when the model contains cubic terms. Especially Metaforests overestimation is substantial when $\beta$ = 0.8 and the estimated model is cubic with $\Delta\tau^{2}_{MF} = 2.92 \pm 2.37$, although all other algorithms also have a $\Delta\tau^{2} > 1$ in these conditions. Interestingly, the Pema algorithms even outperform the RMA algorithm within these conditions. The marginal effects of $\beta$ on $\Delta\tau^{2}$  are shown in image 10. MetaForest seems most affected by the increase in $\beta$, but in general performs better than the Pema algorithms when $\beta$ < 0.8. The RMA algorithm performs best overall.

The marginal effect of the skewness of the data $\alpha$ on $\Delta\tau^{2}$  seems rather minimal. There is a slight decrease in $\Delta\tau^{2}$  as $\alpha$ increases, but it is hardly noticeable. However, this decrease becomes more clear when we add the interaction with the estimated model. Image 12 shows the conditional relationship. The algorithms seem rather unaffected by $\alpha$ for the linear model, and a small general decrease in $\Delta\tau^{2}$  as $\alpha$ increases can be seen in the exponential model. When the interaction model is estimated however, the algorithms seem to benefit as $\alpha$ increases, while for the cubic model, $\Delta\tau^{2}$  first increases as $\alpha$ increases, and afterwards decreases. RMA performs best, followed by Metaforest. The Pema algorithms perform similar, but worst.

The effect of the true $\tau^{2}$ on $\Delta\tau^{2}$  also seemed rather unnoticeable for the RMA and Metaforest algorithm. The tendency for the Pema algorithms on the other hand, was to overestimate $\tau^{2}$ more as the true $\tau^{2}$ increased. Image 12 shows the marginal relationship.

The effect of the number of moderators on $\Delta\tau^{2}$  was not that large either. A small increase in $\Delta\tau^{2}$ can be seen in the RMA and Metaforest algorithm as the number of moderators increase, which is not found for the Pema algorithms. However, A small note that should be made is that the Metaforest algorithm does substantially increase in $\Delta\tau^{2}$  as more moderators are added when the estimated model is cubic. Image 13 shows the interaction between the number of moderators and the estimated model on $\Delta\tau^{2}$ .

The number of studies used in the training data $\kappa$ only had a substantial effect for the Metaforest algorithm. For Metaforest, the $\Delta\tau^{2}$  decreased quite rapidly if $\kappa$ increased, especially when the cubic model was estimated. For the other algorithms, decreasing $\kappa$ seemed to have little to no effect on correctly estimating the residual heterogeneity. Image 14 shows the relationship.

Finally, the average number of observations in the studies did not have a substantial effect on $\Delta\tau^{2}$  Image 15 shows the marginal relationship.

*Variable selection*
To determine the extent to which the algorithms could perform correct variable selection, the proportion true positives [TP] and true negatives [TN] were calculated. There were no differences in variables selected by Highest Density Intervals or Confidence Intervals for both Lasso and Horshoe and so for both algorithm it did not matter whether the Highest Density Interval or Confidence Interval were analyzed. The mean proportions along with the standard deviations on TP and TN are provided. It was found that Metaforest had the highest proportion true positives: $TP_{mf} = 0.98 \pm 0.15$, closely followed by RMA: $TP_{RMA} = 0.96 \pm 0.21$. Horshoe performed slightly better than Lasso;  $TP_{hs} = 0.91 \pm 0.29$; $TP_{Lasso} = 0.89 \pm 0.31$. As for TN, it was found that the pema algorithms performed best: $TN_{hs} = 0.93 \pm 0.16$, $TN_{Lasso} = 0.93 \pm 0.17$, followed by RMA: $TN_{RMA} = 0.89 \pm 0.20$. MF performed worst by a large margin: $TN_{mf} = 0.50 \pm 0.35$ 
Perfomance on TP and TN were very high for all algorithms, with all mean proportions exceeding .89. One exception was the performance on TN for MetaForest, which mean was 0.50. This implies that MetaForest had issues excluding irrelevant moderators from the models. Plots were inspected to determine the effects of the design factors on the proportions. Something different to note is that there seem to be little marginal effects of the design factors on TN, while TP is more affected. It implies that the algorithms are more robust in excluding irrelevant moderators than in including relevant moderators.

Firstly, $\kappa$ only had a marginal positive effect on TP. As $\kappa$ increased, TP also increased. This implies that the ability for all algorithms to attribute positive relevance to relevant moderators increased as the number of studies in the training dataset increased. MetaForest had the highest TP, followed by RMA and lastly Horshoe and Lasso. The increase in TP for higher values of $\kappa$ was steeper for the pema algorithms, however. There also seemed to exist an interaction of $\kappa$ with the estimated model. For the linear and interaction model, the relationship of $\kappa$ seemed relatively linear. At $\kappa = 20$ the TP was relatively low for the algorithms, compared to the cubic model where TP starts at .98 and converges to 1 as $\kappa$ increased. This latter relationship was also found for the exponential model, although the TP at $\kappa = 20$ was slighlty lower. Image 16 shows the interaction.

The mean observations per study had a roughly positive linear relationship with TP for all algorithms. MetaForest performed best, followed by RMA, while Horseshoe and Lasso performed worst. Image 17 shows the relationship.

The true effect size $\beta$ had an interaction effect with the model estimated on TN. Only for the interaction model, TN decreased as $\beta$ increased, For the other models, TN remained stable. This could be because the interaction model was only fitted when there were 3,4 or 7 moderators, while for the other models, only 2,3 or 6 moderators were used. Image 18 shows the relationship. The effect of $\beta$ on TP was positive; as $\beta$ increased, TP increased too.

The true $\tau^2$ had a negative effect on TP, while skewness parameter $\alpha$ seemed to have little effect of both TP and TN. Image 19 shows the marginal relationship of $\tau^2$ on TP.

Finally, there seemed to be an effect of number of moderators on TN only for the interaction model. The TN increased as the number of moderators did. Image 20 shows the relationship. The relationship was reversed for TP and was found for all algorithms, i.e. TP decreased as the number of moderators increased.

>>>>

# Results
There were 3888 condition combinations and for each of those the algorithms ran 100 times, leaving 388800 cases to analyze. Out of those, 20 cases had missing values on all metrics for the RMA algorithm. Closer inspection showed that both the cubic and exponential model each contributed ten times to the missing values and only when 2, 3 or 6 moderators were taken up in the model. However, since these 20 cases make up only 0.005% of the data, the missing values were chosen to be omitted from further analysis. Another observation is that the two-way interaction model only had results when there were either 3,4 or 7 moderators taken up, while the other models only had results when there were 2,3 or 6 moderators. It is therefor more challenging to compare and interpret the effect the moderators had on the performance criteria between the two-way interaction and the other models.

## Predictive performance
Predictive performance was operationalized by calculating the $R^2_{test}$ and $MSE_{test}$ for every combination of design factors, in further test denoted as $R^2$ and $MSE$ respectively. The densities for the $R^{2}_{test}$ and $MSE_{test}$ values were skewed however, which is why it was chosen to use the median $R^2$ as the metric for predictive performance, rather than the mean. The spread of the metrics was described using the Mean Absolute Deviation [MAD], rather than the standard deviation. It was found that the Horseshoe, Lasso and RMA algorithm performed similarly overall, $R^2_{Hs} = 0.51 \pm 0.36$, $MSE_{Hs} = 0.21 \pm 0.18$ ; $R^2_{Lasso} = 0.50 \pm 0.37$, $MSE_{Lasso} = 0.21\pm 0.19$; $R^2_{RMA} = 0.50 \pm 0.37$, $MSE_{RMA} = 0.22 \pm 0.23$ . The MetaForest algorithm performed worst on $R^2$: $R^2_{Mf} = 0.35 \pm 0.38$, $MSE_{Mf} = 0.22 \pm 0.19$

To determine the effect of the design factors on $R^2$ for all algorithms, four separate ANOVA’s were performed, one per algorithm. The effect size $\eta^{2}$ per condition per algorithm, including for all two-way interactions can be found in table 1. Do note that the ANOVA's were performed with the normality assumption violated. The estimates serve mostly as a guidance, rather than an absolute result.

Not too surprisingly, It was found that the true effect size $\beta$ had the largest effect on $R^{2}$ for all algorithms. As $\beta$ increased, the performance of all algorithms increased as well. However, $\beta$ did interact with the model that was estimated, being either a linear, two-way interaction, cubic or an exponential model. The image of the interaction is shown in image 1. When the exponential and cubic model were estimated, the increase of $R^{2}$ slows for every higher value of $\beta$. For the estimation of the two-way interaction model the increase only slowed when $\beta$ goes from 0.5 to 0.8, while the steepest increase for the linear model estimation is when $\beta$ increases from 0.2 to 0.5. Also noteworthy is that $R^2$ stagnates during estimation of the cubic model as $\beta$ goes up to 0.5 and onwards, while the other models do keep increasing. There was little difference in median $R^2$ between Horsehoe, Lasso and RMA, while MetaForest performed worst.

The second largest marginal effect was that of the estimated model. All algorithms had the highest $R^2$ under the cubic model, followed by a similar performance on the two-way interaction and exponential models. All algorithms performed worst for the linear model. There again was little difference in performance between the Pema algorithms and RMA, altough MetaForest performed worst. Image 2 shows the relationship.

There also was a moderate interaction effect between the estimated model and the amount of skewness of the input data $\alpha$, especially for the Pema algorithms. Again, Pema and RMA algorithms performed best, followed by MetaForest in all conditions. Most obvious to note is that all algorithms, except for when the linear model was estimated, generally performed better on more skewed data, although the algorithms did perform worse during estimation of the two-way interaction model and as $\alpha$ goes from 5 to 10. Overall performance was best during estimation of the cubic model, but the performance difference between estimated models decreased as $\alpha$ increased. Image 3 shows the relationship.

The true residual heterogeneity $\tau^{2}$ had a negative linear relationship for all algorithms on $R^{2}$. That is, as $\tau^{2}$ increased, $R^{2}$ decreased. Image 4 shows the relationship.

The mean sample size per study $\bar{n}$ also had a moderate effect. For all algorithms the effect of $\bar{n}$ was positively linearly related with $R^{2}$. Again, the Pema and RMA algorithms performed better than MetaForest. Image 5 shows the relationship.

An especially large effect was found for the number of studies used in the training data $\kappa$ for MetaForest, $\eta^{2} = 0.27$, while this effect was substantially smaller for RMA, $\eta^{2} = 0.11$; Lasso, $\eta^{2} = 0.06$ and; Horseshoe, $\eta^{2} = 0.05$. The relationship is positively linear for all algorithms, but the slope is especially steep for MetaForest. Image 6 shows the relationship.

Finally, the number of moderators did not have a big effect for the Pema algorithms: $\eta^{2} = 0.01$ while for RMA and MetaForest $\eta^{2} = 0.05$. The relationship is shown in image 7. The relationship is generally negative with more moderators meaning worse performance, although an increase can be observed as the number of moderators increase from 4 to 6 for all algorithms except MetaForest. This increase in performance for MetaForest appears when the number of moderators go from 3 to 4.

## Estimating residual heterogeneity
The ability of the algorithms to correctly estimate $\tau^{2}$ was operationalized by subtracting the true value for $\tau^{2}$ from the $\tau^{2}$ estimated by the algorithms. Again, the median and Mean Absolute Deviation were used as metrics for performance. The RMA algorithm showed the best results, $\Delta\tau^2_{RMA} = 0.02 \pm 0.06$, followed by the MetaForest algorithm $\Delta\tau^2_{Mf} = 0.09 \pm 0.13$. The Pema algorithms performed worst $\Delta\tau^2_{Lasso} = 0.23 \pm 0.18$; $\Delta\tau^2_{Hs} = 0.23 \pm 0.17$. The finding that all medians are positive implies that all algorithms have a bigger tendency to overestimate $\tau^{2}$ than underestimate it. One comment to make is that uncertainty of the estimates generally increased as $\Delta\tau^{2}$ also increased. This implies that there was more variation in performance as median performance worsened.

To determine the effect of the design factors on $\Delta\tau^{2}$ for all algorithms, four separate ANOVA’s were performed. The effect size $\eta^{2}$ per condition per algorithm, including $\eta^2$ for all two-way interactions can be found in table 2. Again, the assumption of normality was violated.

The biggest predictor on the correct estimation of $\tau^{2}$ was the estimated model. This was mainly because the algorithms overestimated $\tau^{2}$ most when the model contained cubic terms. Image 8 shows the marginal relationship of the estimated model on $\Delta\tau^{2}$ . It becomes more clear why this overestimation occurred when showing the interaction between $\beta$ and the model estimated on $\Delta\tau^{2}$, shown in image 9. First note the general trend that during estimation of all models $\tau^{2}$ got more overestimated as $\beta$ increased, except during estimation of the linear model, where the effect of $\beta$ on $\Delta\tau^{2}$ was close to zero, except for MetaForest. However, note the scales for the y-axes. While estimating the two-way interaction, linear and exponential model, $\Delta\tau^2$ stayed well within a confined interval. However, the algorithms severely overestimated $\tau^{2}$ when the model contained cubic terms. Especially MetaForest overestimated $\tau^{2}$ substantially when $\beta = 0.8$ and the estimated model is cubic: $\Delta\tau^{2}_{MF} = 2.92 \pm 2.37$. The other algorithms also had a $\Delta\tau^{2} > 1$ in these conditions, but the results were not as severe. Interestingly, the Pema algorithms even outperformed the RMA algorithm in these conditions.

The marginal effects of $\beta$ on $\Delta\tau^{2}$  are shown in image 10. MetaForest was most affected by the increase in $\beta$, but in general performed better than the Pema algorithms when $\beta < 0.8$. The RMA algorithm performed best overall.

The marginal effect of $\alpha$ on $\Delta\tau^{2}$ was rather minimal, altough there was a slight decrease in $\Delta\tau^{2}$ as $\alpha$ increased. However, the decrease is more explicit when the interaction of $\alpha$ with the estimated model is added. Image 11 shows this interaction. The algorithms were rather unaffected by $\alpha$ for the linear model, and a small decrease in $\Delta\tau^{2}$ as $\alpha$ increased can be seen in the exponential model. When the two-way interaction model is estimated however, the algorithms benefitted as $\alpha$ increased, while for the cubic model, $\Delta\tau^{2}$ first increased as $\alpha$ increased from 0 to 2, but decreased as $\alpha$ increased from 2 to 10. RMA performed best, followed by MetaForest. The Pema algorithms performed similarly, but worst.

The effect of the true $\tau^{2}$ on $\Delta\tau^{2}$ was rather unnoticeable for the RMA and MetaForest algorithms. The tendency for the Pema algorithms on the other hand, was to overestimate $\tau^{2}$ more as the true $\tau^{2}$ increased. Image 12 shows the marginal relationship.

The effect of the number of moderators on $\Delta\tau^{2}$  was not that large either. A small increase in $\Delta\tau^{2}$ can be seen in the RMA and MetaForest algorithm as the number of moderators increased, which was not found for the Pema algorithms. However, A small note is that MetaForest did substantially increase in $\Delta\tau^{2}$ as more moderators were added and the estimated model is cubic. Image 13 shows the interaction between the number of moderators and the estimated model.

$\kappa$ only had a substantial effect for MetaForest; the $\Delta\tau^{2}$  decreased quite rapidly if $\kappa$ increased, especially when the cubic model was estimated. For the other algorithms, decreasing $\kappa$ had little to no effect on correctly estimating the residual heterogeneity. Image 14 shows the relationship.

Finally, the average number of observations in the studies did not have a substantial effect on $\Delta\tau^{2}$. Image 15 shows the marginal relationship.

## Variable selection
To determine the extent to which the algorithms could perform variable selection correctly, the proportion true positives [$TP$] and true negatives [$TN$] were calculated. The $TP$ and $TN$ reflect how well the algorithms accredit importance to relevant moderators and discredit importance to irrelevant moderators respectively. It should be noted that $TP$ could only take on values 1 or 0 per simulated iteration, because in all models where $\beta > 0$, only one moderator was simulated to be relevant. As $\beta$ increased, the already relevant moderator increased in relevance, rather than spreading the relevance over the other moderators. $TN$ had a bigger range and could take on values dependent on how many moderators were taken up in the model. E.g. when $\beta = 0$ and $n_{mods} = n$, $n+1$ different proportions were possible, $\frac{0}{n}$ up until $\frac{n}{n}$.

There were no differences in variables selected by Highest Density Intervals or Confidence Intervals for both Lasso and Horshoe and so for both algorithms it did not matter which interval type was analyzed. It was found that MetaForest had the highest proportion true positives: $TP_{Mf} = 0.98$, closely followed by RMA: $TP_{RMA} = 0.96$. Horshoe performed slightly better than Lasso;  $TP_{Hs} = 0.91$; $TP_{Lasso} = 0.89$. As for $TN$, it was found that the pema algorithms performed best: $TN_{Hs} \ \text{and} \ TN_{Lasso} = 0.93$, followed by RMA: $TN_{RMA} = 0.89 \pm 0.20$. MetaForest performed worst by a large margin: $TN_{Mf} = 0.50$. The Mean Absolute Deviation for all algorithms on both $TP$ and $TN$ was 0, except for MetaForests performance on $TN$, where the Mean Absolute Deviation was 0.44.

Perfomance on $TP$ and $TN$ were very high for all algorithms, with all mean proportions, except MetaForests performance on $TN$, exceeding .89. This implies that MetaForest had issues excluding irrelevant moderators from the models. Plots were inspected to determine the effects of the design factors on the proportions. While inspecting the plots, there were found to be little marginal effects of the design factors on $TN$, while $TP$ was more affected.

Firstly, $\kappa$ only had a marginal positive effect on $TP$. As $\kappa$ increased, $TP$ also increased. MetaForest had the highest $TP$, followed by RMA and, lastly, Horsehoe and Lasso. The increase in $TP$ for higher values of $\kappa$ was steeper for the Pema algorithms, however. There was also an interaction of $\kappa$ with the estimated model shown in image 16. During estimation of the linear and two-way interaction model, the relationship of $\kappa$ looked relatively linear. At $\kappa = 20$ the $TP$ was relatively low for the algorithms, compared to the cubic model where $TP$ starts at .98 and converges to 1 as $\kappa$ increased. This latter relationship was also found for the exponential model, although the $TP$ at $\kappa = 20$ was lower.

$\bar{n}$ had a positive and roughly linear relationship with $TP$ for all algorithms. MetaForest performed best, followed by RMA, while Horseshoe and Lasso performed worst. Image 17 shows the relationship.

$\beta$ had an interaction effect with the model estimated on $TN$. Only during estimation of the two-way interaction model, $TN$ decreased as $\beta$ increased, For the other models, $TN$ remained stable. This could be because the interaction model was only fitted when there were 3,4 or 7 moderators, while for the other models, only 2,3 or 6 moderators were used. Image 18 shows the relationship. The effect of $\beta$ on $TP$ was positive; as $\beta$ increased, $TP$ increased too.

The true $\tau^2$ had a negative effect on $TP$, while $\alpha$ seemed to have little effect on both $TP$ and $TN$. Image 19 shows the marginal relationship of $\tau^2$ on $TP$.

Finally, there seemed to be an effect of number of moderators on $TN$, but only for the two-way interaction model. The $TN$ increased as the number of moderators did. Image 20 shows the interaction. This relationship was reversed for $TP$ and was found for all algorithms, i.e. $TP$ decreased as the number of moderators increased.

# Discussion
